% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

\author{}
\date{}

\begin{document}

\hypertarget{david-pierson-bradway-ph.d.}{%
\section{David Pierson Bradway,
Ph.D.~}\label{david-pierson-bradway-ph.d.}}

\href{mailto:david.bradway@duke.edu}{\nolinkurl{david.bradway@duke.edu}}\\
Research Scientist\\
Biomedical Engineering\\
Duke University\\
Durham, NC 27708 USA

\hypertarget{objective}{%
\subsection{Objective}\label{objective}}

\begin{itemize}
\tightlist
\item
  Career in research, visualization, data acquisition, and signal
  processing
\item
  Engineering, research and development role in academia or industry
\end{itemize}

\hypertarget{work-experience}{%
\subsection{Work Experience}\label{work-experience}}

\begin{itemize}
\item
  \textbf{Duke University} (Durham, NC, USA)

  Research Scientist, 2014 - present

  \begin{itemize}
  \tightlist
  \item
    Managing clinical trials on ultrsound imaging in fetal and liver
    clinics
  \item
    Working with graduate students on NIH-funded research
  \item
    Contributed to several funded NIH grant applications
  \end{itemize}
\item
  \textbf{Technical University of Denmark (DTU)} (Kongens Lyngby,
  Denmark)

  Postdoctoral Researcher, 2013 - 2014

  \begin{itemize}
  \tightlist
  \item
    Developed OpenCL software for processing 3-D vector flow imaging
    ultrasound data on the GPU
  \item
    Presented one conference presentation, one poster, and two
    proceedings (SPIE 2014 \& 2015)
  \item
    Contributed as co-author to one peer-reviewed journal articles
  \item
    Examined feasibility of transthoracic cardiac vector flow imaging on
    a phased-array probe
  \end{itemize}
\item
  \textbf{Duke University} (Durham, NC, USA)

  Graduate Research and Teaching Assistant, 2005 - 2013

  \begin{itemize}
  \tightlist
  \item
    PhD project using ultrasound to noninvasively measure the heart's
    mechanical properties
  \item
    Organized and conducted clinical studies at Duke University Medical
    Center
  \item
    Presented results in conferences and proceedings and via
    peer-reviewed journal articles
  \end{itemize}
\item
  \textbf{Siemens Healthcare} (Issaquah, WA, USA)

  Graduate Student Research Intern, 2008

  \begin{itemize}
  \tightlist
  \item
    Worked within a research and development team in a large corporation
  \item
    Added multiple focal zone ARFI excitation to research mode of Acuson
    S2000 ultrasound scanner
  \item
    Learned
    \href{http://www-03.ibm.com/software/products/en/clearcase}{version
    control} and \href{http://www.visualstudio.com/}{MS Visual Studio
    IDE} tools
  \end{itemize}
\end{itemize}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{itemize}
\item
  \textbf{Duke University} (Durham, NC, USA)

  \href{http://bme.duke.edu/grad}{Ph.D.~in Biomedical Engineering}, May
  2013.
\item
  \textbf{The Ohio State University (OSU)} (Columbus, OH, USA)

  \href{http://ece.osu.edu/futurestudents/undergrad}{B.S. in Electrical
  and Computer Engineering}, June 2005.
\end{itemize}

\hypertarget{teaching}{%
\subsection{Teaching}\label{teaching}}

\begin{itemize}
\tightlist
\item
  Co-Instructor, Instructor, Adv. Top. Lab for Grads in BME - Intro. to
  Electronics Biomedical Engineering 790L (2018, 2019)
\item
  Instructor, Ultrasound module of Medical Physics 731 (2015, 2016)
\item
  Guest lecturer, Biomedical Engineering 590 (2016)
\item
  Co-Instructor,~``International Summer School on Advanced Ultrasound
  Imaging'', Technical University of Denmark (June 2015)
\end{itemize}

\hypertarget{grants-and-contracts}{%
\subsection{Grants and Contracts}\label{grants-and-contracts}}

\begin{itemize}
\tightlist
\item
  \href{https://dibs.duke.edu/research/awards/schedule-application}{2019
  Research Germinator Award, Duke Institute for Brain Sciences (DIBS)}
  Ravikanth Velagapudi, PhD, Anesthesiology, School of Medicine; and
  William Huffman and David Bradway, PhD, Biomedical Engineering, Pratt
  School of Engineering. Targeting Autophagy with Non-Invasive Vagal
  Nerve Stimulation to Treat Delirium Superimposed on Dementia.
\end{itemize}

\hypertarget{invention-disclosures-and-patents}{%
\subsection{Invention Disclosures and
Patents}\label{invention-disclosures-and-patents}}

\begin{itemize}
\tightlist
\item
  Duke IDF \#a3348ed7: ``Split Aperture ARFI / SWEI''
\item
  Duke IDF \#540: ``Visual Feedback for Improved Triggered Acquisitions
  for Ultrasound Imaging''
\item
  Trahey, G., Long, W., Hollender, P., Bradway, D., Kakkad, V. and
  Bottenus, N., Duke University, 2021.~Methods, systems and computer
  program products for triggering ultrasound data acquisition. U.S.
  Patent 10,969,487.
\end{itemize}

\hypertarget{honors-and-activities}{%
\subsection{Honors and Activities}\label{honors-and-activities}}

\begin{itemize}
\tightlist
\item
  \href{http://www.whitaker.org/grants/fellows-scholars}{Whitaker
  International Program Scholar} (2013)
\item
  \href{http://www.nsfgrfp.org/}{National Science Foundation Graduate
  Research Fellow} (2005-2008)
\item
  \href{https://goldwater.scholarsapply.org/}{Goldwater Research
  Scholar} (2004-2005)
\item
  \href{http://www.montanadeluz.org/}{Organized engineering design and
  build trip to Honduran orphanage} (2004)
\item
  \href{http://ecos.osu.edu/}{Founded engineering community service
  group at Ohio State} (2003)
\end{itemize}

\hypertarget{professional-activities}{%
\subsection{Professional Activities}\label{professional-activities}}

\begin{itemize}
\tightlist
\item
  Early Career Professional Development in Medical Imaging Workshop,
  SPIE Medical Imaging 2015
\item
  Associate Editor, Ultrasonic Imaging journal (2016-)
\item
  Reviewer for the journals Ultrasound in Medicine and Biology,
  Ultrasonic Imaging, and IEEE Transactions on Medical Imaging
\end{itemize}

\hypertarget{skills}{%
\subsection{Skills}\label{skills}}

\begin{itemize}
\tightlist
\item
  Advanced signal and imaging processing programming: Matlab and Python
\item
  Tools and languages: \href{http://git-scm.com/}{Git}, C/C++,
  OpenCL/CUDA, Docker, Linux
\item
  Problem solving, signal and image analysis, data science, scientific
  computing, and experimental design
\item
  Strong written and verbal communication, data visualization
\item
  Successfully written fellowships, scholarships, proposals
\item
  Personal projects in mobile and embedded systems:
  \href{http://www.arduino.cc/}{Arduino},
  \href{http://www.raspberrypi.org/}{Raspberry Pi}
\end{itemize}

\hypertarget{journal-articles}{%
\subsubsection{Journal Articles}\label{journal-articles}}

{[}1--13{]}

\hypertarget{book-chapters}{%
\subsubsection{Book Chapters}\label{book-chapters}}

{[}14,15{]}

\hypertarget{abstracts-and-proceedings}{%
\subsubsection{Abstracts and
Proceedings}\label{abstracts-and-proceedings}}

{[}16--42{]}

\hypertarget{publications}{%
\subsection*{Publications}\label{publications}}
\addcontentsline{toc}{subsection}{Publications}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-Fahey2008a}{}%
1. Fahey BJ, Nelson RC, Bradway DP, Hsu SJ, Dumont DM, et al. (2008) In
vivo visualization of abdominal malignancies with acoustic radiation
force elastography. Physics in medicine and biology 53: 279--93.
doi:\href{https://doi.org/10.1088/0031-9155/53/1/020}{10.1088/0031-9155/53/1/020}

\leavevmode\hypertarget{ref-Fahey2008c}{}%
2. Fahey BJ, Nelson RC, Hsu SJ, Bradway DP, Dumont DM, et al. (2008) In
vivo guidance and assessment of liver radio-frequency ablation with
acoustic radiation force elastography. Ultrasound in medicine \& biology
34: 1590--603.
doi:\href{https://doi.org/10.1016/j.ultrasmedbio.2008.03.006}{10.1016/j.ultrasmedbio.2008.03.006}

\leavevmode\hypertarget{ref-Nightingale2008}{}%
3. Nightingale K, Palmeri M, Zhai L, Frinkley K, Wang M, et al. (n.d.)
Impulsive acoustic radiation force: imaging approaches and clinical
applications. The Journal of the Acoustical Society of America 123:
3792. doi:\href{https://doi.org/10.1121/1.2935460}{10.1121/1.2935460}

\leavevmode\hypertarget{ref-Nightingale2009}{}%
4. Nightingale K, Palmeri M, Dahl J, Bradway D, Hsu S, et al. (2009)
Elasticity imaging with acoustic radiation force: Methods and clinical
applications. Japanese journal of medical ultrasonics 36: 116.

\leavevmode\hypertarget{ref-Wolf2011}{}%
5. Wolf PD, Eyerly SA, Bradway DP, Dumont DM, Bahnson TD, et al. (2011)
Near real time evaluation of cardiac radiofrequency ablation lesions
with intracardiac echocardiography based acoustic radiation force
impulse imaging. The Journal of the Acoustical Society of America 129:
2438. doi:\href{https://doi.org/10.1121/1.3587978}{10.1121/1.3587978}

\leavevmode\hypertarget{ref-Eyerly2012}{}%
6. Eyerly SA, Bahnson TD, Koontz JI, Bradway DP, Dumont DM, et al.
(2012) Intracardiac acoustic radiation force impulse imaging: A novel
imaging method for intraprocedural evaluation of radiofrequency ablation
lesions. Heart rhythm: the official journal of the Heart Rhythm Society
9: 1855--1862.
doi:\href{https://doi.org/10.1016/j.hrthm.2012.07.003}{10.1016/j.hrthm.2012.07.003}

\leavevmode\hypertarget{ref-Hollender2013}{}%
7. Hollender P, Bradway D, Wolf P, Goswami R, Trahey G (2013)
Intracardiac acoustic radiation force impulse (arfi) and shear wave
imaging in pigs with focal infarctions. IEEE transactions on
ultrasonics, ferroelectrics, and frequency control 60: 1669--1682.
doi:\href{https://doi.org/10.1109/TUFFC.2013.2749}{10.1109/TUFFC.2013.2749}

\leavevmode\hypertarget{ref-Patel2014}{}%
8. Patel V, Dahl JJ, Bradway DP, Doherty JR, Lee SY, et al. (2014)
Acoustic Radiation Force Impulse Imaging (ARFI) on an IVUS Circular
Array. Ultrasonic Imaging 36: 98--111.
doi:\href{https://doi.org/10.1177/0161734613511595}{10.1177/0161734613511595}

\leavevmode\hypertarget{ref-Eyerly2014}{}%
9. Eyerly SA, Bahnson TD, Koontz JI, Bradway DP, Dumont DM, et al.
(2014) Contrast in Intracardiac Acoustic Radiation Force Impulse Images
of Radiofrequency Ablation Lesions. Ultrasonic Imaging 36: 133--148.
doi:\href{https://doi.org/10.1177/0161734613519602}{10.1177/0161734613519602}

\leavevmode\hypertarget{ref-jensen2016}{}%
10. Jensen JA, Rasmussen MF, Pihl MJ, Holbek S, Villagómez HCA, et al.
(2016) Safety assessment of advanced imaging sequences i: Measurements.
IEEE transactions on ultrasonics, ferroelectrics, and frequency control
63: 110--119.
doi:\href{https://doi.org/10.1109/TUFFC.2015.2502987}{10.1109/TUFFC.2015.2502987}

\leavevmode\hypertarget{ref-bottenus2016}{}%
11. Bottenus N, Long W, Zhang H, Jakovljevic M, Bradway D, et al. (2016)
Feasibility of swept synthetic aperture ultrasound imaging.
doi:\href{https://doi.org/10.1109/TMI.2016.2524992}{10.1109/TMI.2016.2524992}

\leavevmode\hypertarget{ref-Long2017umb}{}%
12. Long W, Hyun D, Roy Choudhury K, Bradway D, McNally P, et al. (2018)
Clinical utility of fetal short-lag spatial coherence imaging.
Ultrasound in Medicine and Biology 44: 794--806.
doi:\href{https://doi.org/10.1016/j.ultrasmedbio.2017.12.006}{10.1016/j.ultrasmedbio.2017.12.006}

\leavevmode\hypertarget{ref-Flint2020}{}%
13. Flint K, Bottenus N, Bradway D, McNally P, Ellestad S, et al. (2021)
An Automated ALARA Method for Ultrasound: An Obstetric Ultrasound
Feasibility Study. Journal of Ultrasound in Medicine 40: 1863--1877.
Available:
\url{https://onlinelibrary.wiley.com/doi/abs/10.1002/jum.15570}.

\leavevmode\hypertarget{ref-dobbins2019medical}{}%
14. Dobbins JT, Frush DP, Kigongo CJ, MacFall JR, Reiman RE, et al.
(2019) Medical imaging safety in global health radiology. In: Radiology
in global health. Springer. pp. 85--105.

\leavevmode\hypertarget{ref-eyerly2018acoustic}{}%
15. Eyerly-Webb SA, Vejdani-Jahromi M, Kakkad V, Hollender P, Bradway D,
et al. (2018) Acoustic radiation force-based ultrasound elastography for
cardiac imaging applications. In: Ultrasound elastography for biomedical
applications and medicine. John Wiley \& Sons. pp. 504--519.

\leavevmode\hypertarget{ref-Hsu2007c}{}%
16. Hsu SJ, Bradway DP, Fahey BJ, Trahey GE (2007) Transthoracic
Acoustic Radiation Force Impulse Imaging of the Cardiac Cycle. In:
Ultrasonic measurement and imaging of tissue elasticity.

\leavevmode\hypertarget{ref-Bradway2007}{}%
17. Bradway DP, Hsu SJ, Fahey BJ, Dahl JJ, Nichols TC, et al. (2007)
6B-6 Transthoracic Cardiac Acoustic Radiation Force Impulse Imaging: A
Feasibility Study. IEEE. pp. 448--451.
doi:\href{https://doi.org/10.1109/ULTSYM.2007.121}{10.1109/ULTSYM.2007.121}

\leavevmode\hypertarget{ref-Fahey2007b}{}%
18. Fahey BJ, Nelson RC, Hsu SJ, Bradway DP, Dumont DM, et al. (2007)
6B-4 In Vivo Acoustic Radiation Force Impulse Imaging of Abdominal
Lesions. In: 2007 ieee ultrasonics symposium proceedings. IEEE. pp.
440--443.
doi:\href{https://doi.org/10.1109/ULTSYM.2007.119}{10.1109/ULTSYM.2007.119}

\leavevmode\hypertarget{ref-Bradway2009}{}%
19. Bradway DP, Fahey BJ, Nelson RC, Trahey GE (2009) ARFI imaging of
abdominal ablation and liver lesion biopsy. In: International symposium
on ultrasonic imaging and tissue characterization, 2009. Available:
\url{http://uitc-symposium.org/2009_abstracts.pdf}.

\leavevmode\hypertarget{ref-Husarik2009}{}%
20. Husarik DB, Nelson RC, Bradway DP, Fahey BJ, Nightingale KR, et al.
(2009) First Clinical Experience with Sonographic Elastography of the
Liver Using Acoustic Radiation Force Impulse (ARFI) Imaging. In: RSNA.
Available: \url{http://rsna2009.rsna.org/search}.

\leavevmode\hypertarget{ref-Nelson2009}{}%
21. Nelson RC, Bradway DP, Fahey BJ, Trahey GE (2009) Future Application
of Ultrasound: Acoustic Radiation Force Impulse (ARFI) Imaging. In:
AIUM. Available:
\url{http://www.aium.org/loginRequired/membersOnly/proceedings/2009.pdf}.

\leavevmode\hypertarget{ref-Bradway2009b}{}%
22. Bradway DP, Fahey BJ, Nelson RC, Trahey GE (2009) Recent Clinical
Results of Acoustic Radiation Force Impulse Imaging of Abdominal
Ablation. In: International tissue elasticity conference. Available:
\url{http://www.elasticityconference.org/prior_conf/2009/PDF/2009Proceedings.pdf}.

\leavevmode\hypertarget{ref-Hsu2010}{}%
23. Hsu SJ, Bradway DP, Bouchard RR, Hollender PJ, Wolf PD, et al.
(2010) Parametric pressure-volume analysis and acoustic radiation force
impulse imaging of left ventricular function. In: 2010 ieee
international ultrasonics symposium. IEEE. pp. 698--701.
doi:\href{https://doi.org/10.1109/ULTSYM.2010.5935661}{10.1109/ULTSYM.2010.5935661}

\leavevmode\hypertarget{ref-Hollender2010}{}%
24. Hollender PJ, Bouchard RR, Hsu SJ, Bradway DP, Wolf PD, et al.
(2010) Intracardiac measurements of elasticity using Acoustic Radiation
Force Impulse (ARFI) methods: Temporal and spatial stability of shear
wave velocimetry. In: 2010 ieee international ultrasonics symposium.
IEEE. pp. 698--701.
doi:\href{https://doi.org/10.1109/ULTSYM.2010.5935946}{10.1109/ULTSYM.2010.5935946}

\leavevmode\hypertarget{ref-Bradway2010}{}%
25. Bradway DP, Hsu SJ, Wolf PD, Trahey GE (2010) Acoustic Radiation
Force Impulse Imaging of Acute Myocardial Ischemia and Infarct. In:
International symposium on ultrasonic imaging and tissue
characterization. Available:
\url{http://uitc-symposium.org/2010_abstracts.pdf}.

\leavevmode\hypertarget{ref-Bradway2010b}{}%
26. Bradway DP, Hsu SJ, Wolf PD, Trahey GE (2010) Transthoracic Acoustic
Radiation Force Impulse Imaging of Cardiac Function. In: International
tissue elasticity conference. Available:
\url{http://www.elasticityconference.org/prior_conf/2010/PDF/2010Proceedings.pdf}.

\leavevmode\hypertarget{ref-Bradway2011}{}%
27. Bradway DP, Rosenzweig SR, Doherty JR, Hyun D, Trahey GE (2011)
Recent Results and Advances in Transthoracic Cardiac Acoustic Radiation
Force Impulse Imaging. In: International symposium on ultrasonic imaging
and tissue characterization. Available:
\url{http://www.elasticityconference.org/prior_conf/2011/PDF/2011ITECProceedings.pdf}.

\leavevmode\hypertarget{ref-Byram2011}{}%
28. Byram BC, Gianantonio DM, Bradway DP, Hyun D, Jakovljevic M, et al.
(2011) Direct in vivo Myocardial Infarct Visualization Using 3D
Ultrasound and Passive Strain Contrast. In: International tissue
elasticity conference. Available:
\url{http://www.elasticityconference.org/prior_conf/2011/PDF/2011ITECProceedings.pdf}.

\leavevmode\hypertarget{ref-Byram2011b}{}%
29. Byram BC, Bradway DP, Jakovljevic M, Gianantonio D, Hyun D, et al.
(2011) Direct In Vivo Myocardial Infarct Visualization Using 3D
Ultrasound and Passive Strain Contrast. In: IEEE ultrasonics symp.
doi:\href{https://doi.org/10.1109/ULTSYM.2011.0007}{10.1109/ULTSYM.2011.0007}

\leavevmode\hypertarget{ref-Bradway2012}{}%
30. Bradway DP, Hollender PJ, Goswami R, Wolf PD, Trahey GE (2012)
Feasibility and safety of transthoracic cardiac acoustic radiation force
impulse imaging methods. In: 2012 ieee international ultrasonics
symposium. IEEE. pp. 2027--2030.
doi:\href{https://doi.org/10.1109/ULTSYM.2012.0507}{10.1109/ULTSYM.2012.0507}

\leavevmode\hypertarget{ref-Bradway2012b}{}%
31. Bradway DP, Hollender PJ, Goswami R, Wolf PD, Trahey GE (2012)
Transthoracic Cardiac Acoustic Radiation Force Impulse Imaging: in vivo
Feasibility, Methods, and Initial Results. In: International symposium
on ultrasonic imaging and tissue characterization, 2012. Available:
\url{http://uitc-symposium.org/2012_abstracts.pdf}.

\leavevmode\hypertarget{ref-Hollender2012}{}%
32. Hollender PJ, Bradway DP, Goswami R, Wolf PD, Trahey GE (2012)
Acoustic radiation force techniques for imaging cardiac infarct in vivo:
methods and initial results. In: International symposium on ultrasonic
imaging and tissue characterization. Available:
\url{http://uitc-symposium.org/2012_abstracts.pdf}.

\leavevmode\hypertarget{ref-Eyerly2012b}{}%
33. Eyerly SA, Bahnson T, Koontz J, Bradway DP, Dumont DM, et al. (2012)
Confirmation of Cardiac Radiofrequency Ablation Treatment Using
Intra-Procedure Acoustic Radiation Force Impulse Imaging. In: IEEE
ultrasonics symposium.
doi:\href{https://doi.org/10.1109/ULTSYM.2012.0509}{10.1109/ULTSYM.2012.0509}

\leavevmode\hypertarget{ref-Hollender2012b}{}%
34. Hollender PJ, Bradway DP, Wolf PD, Goswami R, Trahey GE (2012)
Intracardiac ARF-driven Shear Wave Velocimetry to Estimate Regional
Myocardial Stiffness and Contractility in Pigs with Focal Infarctions.
In: IEEE ultrasonics symposium.
doi:\href{https://doi.org/10.1109/ULTSYM.2012.0508}{10.1109/ULTSYM.2012.0508}

\leavevmode\hypertarget{ref-Goswami2013}{}%
35. Goswami R, Bradway D, Kisslo J, Trahey G (2013) Novel Application of
Acoustic Radiation Force Impulse Imaging in Transthoracic
Echocardiography. In: Journal of the american college of cardiology.
American College of Cardiology Foundation, Vol. 61. p. E1090.
doi:\href{https://doi.org/10.1016/S0735-1097(13)61090-6}{10.1016/S0735-1097(13)61090-6}

\leavevmode\hypertarget{ref-Patel2013}{}%
36. Patel V, Dahl JJ, Bradway DP, Doherty JR, Smith SW (2013) Acoustic
radiation force impulse imaging on an IVUS circular array. In: 2013 ieee
international ultrasonics symposium (ius). IEEE. pp. 773--776.
doi:\href{https://doi.org/10.1109/ULTSYM.2013.0199}{10.1109/ULTSYM.2013.0199}

\leavevmode\hypertarget{ref-Bradway2014}{}%
37. Bradway DP, Pihl MJ, Krebs andreas, Tomov BG, Kjær CS, et al. (2014)
Real-time GPU implementation of transverse oscillation vector velocity
flow imaging. In: SPIE medical imaging.Vol. 9040. pp. 90401Y--90401Y--6.
doi:\href{https://doi.org/10.1117/12.2043582}{10.1117/12.2043582}

\leavevmode\hypertarget{ref-Bradway2015}{}%
38. Bradway DP, Hansen KL, Nielsen MB, Jensen JA (2015) Transverse
oscillation vector flow imaging for transthoracic echocardiography. In:
SPIE medical imaging. pp. 941902--941902--7.
doi:\href{https://doi.org/10.1117/12.2081145}{10.1117/12.2081145}

\leavevmode\hypertarget{ref-Bottenus2015}{}%
39. Bottenus N, Long W, Bradway D, Trahey G (2015) Phantom and in vivo
demonstration of swept synthetic aperture imaging. In: 2015 ieee
international ultrasonics symposium (ius). pp. 1--4.
doi:\href{https://doi.org/10.1109/ULTSYM.2015.0075}{10.1109/ULTSYM.2015.0075}

\leavevmode\hypertarget{ref-Kakkad2015}{}%
40. Kakkad V, Kuo L, Bradway D, Trahey G, Sivak J, et al. (2015) In vivo
transthoracic measurements of acoustic radiation force induced
displacements in the heart over the cardiac cycle. In: 2015 ieee
international ultrasonics symposium (ius). pp. 1--5.
doi:\href{https://doi.org/10.1109/ULTSYM.2015.0155}{10.1109/ULTSYM.2015.0155}

\leavevmode\hypertarget{ref-Kakkad2017}{}%
41. Kakkad V, Ferlauto H, Bradway D, Heyde B, Kisslo J, et al. (2017)
Clinical feasibility of a noninvasive method to interrogate myocardial
function via strain and acoustic radiation force-derived stiffness. In:
IEEE international ultrasonics symposium, ius.
doi:\href{https://doi.org/10.1109/ULTSYM.2017.8092067}{10.1109/ULTSYM.2017.8092067}

\leavevmode\hypertarget{ref-Hollender2017}{}%
42. Hollender P, Bottenus N, Bradway D, Trahey G (2017) Single track
location comb-push ultrasound shear elastography (STL-CUSE). In: IEEE
international ultrasonics symposium, ius.
doi:\href{https://doi.org/10.1109/ULTSYM.2017.8092809}{10.1109/ULTSYM.2017.8092809}
\end{cslreferences}

\end{document}
